What I said is both of them.
We have a site that is going to help me.
So we put money from Santosh.
And I do not have any chance at impersonation.
I do not have impersonation.
I speak to my brother.
Hello, my brother.
I don't have any chance at impersonation.
I don't have any chance at impersonation.
I can tell you the number.
I mean, on the table where we are signing the document,
I'll write that number.
No, please understand.
No, sir.
Nobody is understanding.
The table when we sit to sign the document,
all of these what we are discussing,
has to be concluded in a proper way.
And that only will sit for the NOCN signatures.
Before that, because you need to confirm,
it's not that once we agree only for sign-off on the document,
then only you will do the wave of no.
You have to first assure and of course,
we will also go ahead and discuss with owners
and we'll get back on that.
Because ultimately, today, tomorrow, after three months,
six months, we have to take the handover.
We cannot deny that.
We will definitely get back on that.
But we need all of these clauses to be met
in order for us to proceed.
And even it can't be a cross-room,
two people having a conversation.
All the owners have to know.
Exactly.
It can't be that you sit in one time and discuss.
We propose a proposal to the association.
The association will let take it away.
No, sir.
No, sir.
No, sir.
We can talk to the owners.
Yes, we can talk to the owners.
Okay, sure.
No, sir.
No, sir.
How many were there?
No, sir.
Because we cannot...
There is already a lot of tension within the...
Sir, one thing we'll tell you...
...a little bit through association only.
We're going to let it be transparent.
Whatever.
I'm giving the...
No, sir.
Can you sign it now?
Can you sign it now?
That anyway will not happen.
No, one second.
I...
No, no, one second.
You're not going to say that.
Please sign.
No, one second.
All the points and agenda today...
...you give us a satisfactory response for each of those.
We are ready to at least give you assurance...
...that yes, we will sign off as soon as possible.
But are you ready to give all the satisfactory assurance?
Yes.
That's what he's saying.
That's what he's telling.
That's what I'm saying.
That's what he's telling.
That's what I'm saying.
If he agrees to resolve it right away...
What problem do we have?
We'll take it.
Even then, handover has to be...
...if photo gets done.
Exactly.
Photo gets done.
Exactly.
That comes on you, right?
Yes, of course.
Photo is a part of...
No, no.
Praveen.
Praveen.
Photo is a part of that agenda.
So that also is included in the same.
Conditional approval.
We are ready to do it.
Why don't we do it?
We know that we have to do it.
Let's move on to the next point.
No, we have no...
How can we move on?
Give us a number.
Give us a number.
Without number, how can we move on?
Okay, next point is the common area.
See that.
Nothing.
We have to check the cost.
We have to check the GFP.
What did I tell you yesterday?
The contract approval is a major factor...
...that's the actual reason.
Sorry, sorry, sorry.
No, we can't tell you.
We have to come here.
We want a resolution.
You said...
I will ensure also people who need to be...
...resolution are there.
That's why we are meeting here.
Otherwise, what did I say?
We will come to corporate office.
Because we wanted to meet all the decisions.
Okay, anyone?
We need a decision-maker.
He is a decision-maker.
He is a decision-maker.
We have to make cost estimate.
He is not a decision-maker.
Check with GFP.
Check with GFP.
I need to go to management.
Why?
I've told you the decision.
That doesn't mean that...
...every decision will be close to you.
That's the decision of management.
That is the problem.
No, no.
The problem here is you have not told us...
...what that is.
What we are requesting you...
...you work with GFP and get the remaining money.
I am flexible enough to tell that...
...I will absorb some part of trust.
And the rest of the part...
...GFP should absorb.
That itself is a big achievement...
...for any association.
Sir.
I mean, that is a P\&R of any project...
...which are...
Sir, it's been looking at us...
...from what angle do you see the premium?
Which is why we have come and bought the property there.
If this was a life-road project...
...you could have told all that to me.
Right?
This is something that we have looked at...
...from a budget-homing standpoint.
So, you can't be taking more money from us.
We don't have the money.
I don't have the money.
I don't have the money.
I don't have the company.
I don't have any money to pay you...
...for the next one month.
Now, I might have to say...
...I don't have the money.
Do what you can.
I'm requesting you.
If you don't do, then we'll figure it out.
Right?
That's the only option here.
You're not coming to a point of saying...
...that, okay, I'll speak to GLP here...
...and get the deficit that we have.
You have an approved budget for this amount...
...for whatever new discussions you have.
The remaining gap...
...you ask GLP to pay you.
They are the ones who are...
No, I think he's saying that...
...he'll speak to you directly.
I don't have to.
I don't.
That's the third party.
I'd love to go on speaking to them.
You speak to them and come back.
Everybody has to pay a price for you.
So, fine.
Now, you get knowledge.
Getting people to explore you.
Fine.
Let's conclude this.
You will have your cost.
You will check with GLP director.
You'll get back in the next one day.
Is that fine?
A plus B, yeah.
A plus B, done.
Point number one, should we conclude?
Should we move on to the next one?
We are wasting time also.
Conclude as in...
...he has to get back with a...
That's what I'm saying.
And even before that...
...not sending the legal...
...which is protocol, right?
He's sending the legal invoice to the owner...
...for two months and all.
We don't want that.
Don't do that.
No.
I'll be very transparent.
That will go to...
So, one second.
What does that mean to the owner?
It says about what is happening...
...and what is current rate...
...when our funds are getting...
So, fine.
We are okay with that.
But you need to also...
No, one second.
One second.
Let them justify.
Let them justify why?
Because we'll have that as an evidence for future.
Why?
Let them justify.
No.
Yeah.
That's not a legal letter.
Is that a legal letter?
Different.
Is that a legal letter?
Yeah, he's saying legal letters.
Yeah, he's saying legal letters.
Okay, fine.
No, this is a legal letter.
That's an email.
That's an email which...
It's not a legal letter.
The email approved by legal...
...will be sent to...
No, sir.
That's not legal.
No, it is signed...
...approved by legal.
Okay.
Let's not get into that.
Otherwise, we all will have to...
...come and sit over here, sir.
No.
Here and all of the...
How are you going to adopt this?
Where do I sit?
So, yeah, we need to hold on to it...
...until...
...and this is getting...
...more than 50% of owners are...
See, I was just saying...
...automizing the cost.
200,000...
I can't...
So, whoever is holding...
...so they can let them...
...hold on to it.
So, you hold on to it.
We can...
Why this is being described?
Hold on to it.
We don't have to run around...
...on this.
See, coffee...
We can...
Don't sign it for now.
Don't sign it.
Because, right now, let the discussion happen...
...let the decisions be done.
Why would you sign it?
Anyway, why would you sign it?
Generally, you will come back in a day, man.
And just this whole...
...this whole email for a day.
No.
No, no, no.
Forget about it.
We've got all the properties in the back door.
We've got all the...
That's all.
That's all.
That's all the way it hurts.
100% of owners...
...like 40 people, 50 people standing...
...and giving videos or anything like that.
They will not care going to court.
They have to get a message...
...from Bangalore to court...
...of the company.
I'm telling you...
...let us solve the problem.
That is what he said.
He's not saying anything different.
He said, first optimize the cause...
...then speak to GPL...
...to see how much you know that we can absorb.
So, don't send anything today.
If you send some emails today...
Hold on to that.
There's no point of meeting.
Hold on to that.
What is the point of that email?
We are going to absorb it anyway.
Hold on to that email.
Hold on to that email.
Let us discuss all this for the next two days.
Hold on to it.
You get this.
What are you coming up with?
Tomorrow, you have to get back to us on that.
Please.
So, Prasad has just started from Indra Nagar project.
He will take one more hour to reach.
No, I think...
...the boards have so much time.
We all have offices to attend to.
We have to thank each other.
Yeah, yeah.
Another 10 minutes, please.
10-15 minutes, please.
I have to go.
I can order all lunch for you.
No, sir, sir...
1 second...
One second...
Put that in the maintenance.
That's what I was going to just say.
Direct that amount from that.
Yeah, yeah, yeah.
Put it back to the maintenance. We don't want power and all to be discussed.
150th or will you?
I think it will go for one more hour. We will discuss all the points.
All your asks, you keep it very crisp when Prasad comes. Let us not again start all of this.
I will tell you, we talked about this one.
My response also to you. Please we will tell. This is my response. Let Prasad decide.
So the first one we discussed, responses tomorrow you will come back, correct?
Yes.
What is the second one?
Drainage.
Drainage to give a lighter.
STP.
The lighter needs to be modified.
Yeah.
Because Manita LLT is a sherry company. We want the name GBM, not Manita.
Correct.
We will send it to you. You review and give us the letter.
No, sorry. I did not get it.
So I reviewed what are the letter head sherry positions.
Not the final one.
So there it says if Manita, upcoming Manita project constructs a drainage system, we will
connect that, we will project to that.
So it says that there is a dependent on the grant budget?
There is a dependent on the grant budget.
And there is no responsibility in that?
So basically that is not what we need is, the letter clearly says, should say, GPL will
actively take the responsibility if any of the government authorities or relevant authorities
to this particular STP, in case if someone finds a case or someone panelizes due to excess
water point or for whatever there is, whatever we are discussing.
So we need that kind of assurance.
Complete account table.
And also making a provision.
This is just for our assurance.
And also making a provision in the near future.
We need the name of Manita.
Because after five years, this is a self company result.
We need the name GP.
The accountability until the drainage is done.
First we have agreed to give an email from you guys tonight.
No, we do not want an email.
Let me.
Then we told, I mean other GPL employees will give an email.
That also told emails will not pressed.
Then we agreed for a letter head to you.
Now we are dictating what to write in the letter.
No sir.
The content.
Let me.
This is a sequence of issues.
I mean any company, any real estate.
No, but we never asked only for email.
I think it was Junaid's assumption that he said that will suffice.
We said no.
Legally, any email from Gozre's properties.
No, that's fine.
But what I am saying is, it was.
First of all, we have no time to file with Gozre's GPL.
With all intents and only this is being asked.
No.
I must try.
Otherwise, we have fulfilled the project.
No sir.
I meant in other projects.
Here if you are asking for.
I have agreed for it.
But in a different way.
GPL is not taking any responsibility.
It is saying that at the will and fancy of the Panchayat.
Whenever they connect, we will have, I understand.
But the rest will be a responsibility.
And what is happening sir in the market?
The builder exits.
There are fines and all that kind of headaches that come from compliance parties.
I will show you examples, live examples from my own friends who are in other buildings.
Best comp will come, pollution mode will come, all of them will come after you exit.
Because you had some understanding with them until you are exiting the first year.
Second year onwards, we want to live peacefully.
We don't want to be paying 50 crores, 20 lakhs, 50 lakhs to these agencies.
That is where we want your assurance.
Because you have not done your work.
Sir, I am not degraded in anywhere.
See, you took aqua example.
Can you refer any of our projects?
Sorry.
If we are an IHC builder, I accept their pay.
Because they deviate themselves.
Sir, right now you have come to the south very recently.
You are expanding aggressively through LLP.
No, no.
Currently if you look at the trend also, the last few.
Under the Parker tree, 24, aqua, all these are recent projects.
It's not like you've been here for 40 years.
You are expanding aggressively.
You are expanding aggressively.
So the challenge is these may not come out immediately.
Nobody shares it also.
Because there is a fear among owners that the moment I say my story, my property value comes down.
So it is a mind game then.
No, no, no.
We are also aware that if it is one percent, Tico will talk 100 about it.
Yes.
So they are not hiding it.
I am not saying Godrej has had that example.
But that is a trend.
So we have every right to feel afraid and save car.
What is it that we are signing up for?
And we do.
Mr. Hemant, if you are so confident that we have not done anything wrong,
what is the problem in giving this one?
This to add the whole accountability until the trend is formed.
Adding to the issue, recently two or three villages, neighbor villages,
they went and complained to the care we need.
Some native came to inspect.
They expected that.
Some inspector has come.
But they have not seen the way they were.
We have seen the contact scenario.
I was just given a 85.
Some people were there from the...
G.R.P.L. was there.
G.R.P.L. was there.
G.R.P.L. was there.
G.R.P.L. was there.
Some were there from the...
When the lady came to inspect...
I was there.
He was there.
He was there.
He was there.
He was there.
The villagers have started complaining.
It's not the owners who have something.
That event is being handled by legal head, Sami.
Sami has handled that.
No, sir.
That was a provision given that you can connect it to the Rajkara way,
whichever is closed by.
People were ready to do that.
We can partner with him and do that, right?
Why are we not doing it?
Why are we leaving it to the open?
I'll tell you one important point.
Rajkara thing is not legally correct.
We have checked that people are doing it.
But it is like polluting the Rajkara way.
That is not correct.
Okay.
Hence we have not backed out from that.
So then there has to be a lobby from your side
who will work with the Pachai.
The only provision is Nala.
I mean the only train and system.
Correct.
I mean that we have completed depending on the Pachai.
Whatever we have to do, we are already given.
Even for the road development also.
Local authorities say,
was there just not given us anything.
We are not saying it.
We are not saying it.
For every change.
We went, requested the local bodies also, sir.
We are not just moping them.
I wanted to consider that.
Even Santosh was telling us, we will touch with something.
Can we see if with Pachai, you and me are saying this.
We are not together going to Pachai.
They said, till enmity this road is good
because they have given and they have taken care.
Both of them are not care to take care of anybody.
Hence, this is what your state is.
You should go ask them.
We asked them.
You should go ask GPL.
They have taken your money and they are going on from there.
I mean, I am not saying that is true.
But that is the concept.
We will listen from them.
See, check to check.
There might be a...
That is what we face.
The person who were paid would have changed.
That is a new person.
Again, the demand will do.
We have to explain to someone saying,
that person has done that.
We are not saying you have not paid for it
because you also want to sit from here.
Exactly.
You don't want to sit here and listen.
Okay.
I think on that later actually,
the content, what we were demanding.
Exactly.
You want on that later.
Accountability.
We want immunity basically.
Accountability.
The drainage is done.
I was very clear in my last meeting also.
With RK, I committed.
I will give you the letter RK.
No, no.
But the draft, what we received.
Draft?
Accountability.
Until the drainage is done.
That is finished.
This is our second time.
This is not our first time actually.
That is done.
Second time when we put it down,
I replied that we have put the accountability word.
No, but it is not accountability.
Until...
The drainage is formed.
Yeah.
The accountability you are taking.
That goes...
The pollution, the ground material is deep.
Then you take the accountability.
Till then, what will happen?
So, suppose if the grandpa that takes two years.
From the drainage.
Till two years, what will happen?
So, I will just read through.
I understand his...
Godrej, Godrej is ready to take accountability.
For any future consequences pertaining to this STP drainage,
which is clearly mentioned.
And then you have to clearly mention,
until the final drainage provision is made by Godrej or Manita.
Through an approval of local regulators.
So, this line should be that you are taking accountability
for any future consequences,
until final provision is made with a regulatory approval.
You are confident.
You will mention these things.
Everything is fine.
I will write it.
We believe you.
You can write it.
Just write it.
I will put it in a different way.
We will discuss and we will send the following.
You also believe it.
Not that blindly we are asking her.
You are not going to believe it.
You also believe from your side.
Anything me and this guy are not capable to give,
unless and until my legal come forward.
Exactly.
My legal will be held by it.
We have to do that.
You review and cut back first.
No, sir.
90% of the person did not want to believe it.
Like, they don't want to believe it.
They have to say something.
Something comes up.
As an association, we don't have the capacity to deal that.
That's what we are asking.
Sir, are there any association to deal with?
That is the case.
All the projects we only deal.
That's what my persons...
Yes, sir.
What do you think we have to also...
Let's move on to the next point.
They are ready to do it.
The draft will share.
The draft will send you an email.
The draft will send you an email.
Yes, yes.
Next point is common area.
Can you share the draft email with the legal and the...
Yes.
But already actually, I think we have...
The draft was sent.
We have given him the deal.
He has got something.
We will take a...
Send it across to us.
Send it to us or send it to him directly.
No problem.
Copy us and let him review and get it done through his...
Yes.
Fine.
Second point done.
Third...
All the projects that were mentioned to you from so many emails that has been coming in...
We have been raising, right?
The few of the problems which I have listed yesterday in the agenda was one of...
One was this.
You need to put something to...
You know, that jerk needs to get reduced.
It's still there.
Lift.
You need to get that jerk.
We are doing it.
We are doing it.
We are doing it.
Don't change it.
Third point.
The first is lift.
Lift, jerk.
It is the maximum which an...
Not the developer, that service forward can do.
I mean, it is...
They are given us in the writing saying this is the...
As per the highest standard, this is the maximum.
They have read the testing and give us the report.
Anyway, that will come in the audit.
But you have to give that in an audit.
If anything goes south, you will financial handover happen.
Yeah, yeah, of course.
We are not talking about handover.
No, we have...
Every asset will be as per the compliance.
No, no, no.
We will be...
What is the...
No, no.
In audit, if anything comes like...
It is not as per the standards or some division is there.
You have to take the responsibility to rectify that.
That's also I am telling you.
Audit, then, I mean, he will give you some 10,000 points.
Okay.
I am not able to do that all the 10,000 points.
I am telling you all.
Okay.
Whatever is the valid, whatever is the compliance in last year,
I will definitely adhere.
Okay.
Because that guy is getting paid just because he will just
throw the random thing and go.
So I am not able to go.
Okay.
Okay, fine.
We will do the audit and we will get paid.
Second point.
Second is this common area name transfer.
Common area name transfer.
I told you this is the logic.
I think he is not willing to buy that.
See, that is as per my legal opinion.
That is what they had to respond to.
So there is nothing.
So there is nothing.
Conveyions...
Conveyions recently come into this cover.
Yes.
Yeah, before.
Yeah.
So what will happen to previous projects?
That they will figure it out.
Correct.
So when a government, SRO, when a land is given,
or also registered, there will be SRO and there will be
a revenue department who will take the stamp duty
and register.
So when they both are fine and they are okay to exhibit
the sale deed and I mean transfer.
Absolutely.
They will bifurcate the Kata,
the whole land Kata and to the customer.
So are you saying that the whole land Kata has already
been transferred to each individual unit?
It has been bifurcated.
Bifurcated even for the common area?
Common area has been loaded.
That is what I am telling you.
So what does loaded mean?
What does loaded mean?
No, no, no, no, no.
No, no, one second.
Let's understand this.
So this one is a great common area Kata.
Correct.
There will only be land Kata.
Yes.
It includes entire land.
Yes.
Which includes your common area loader,
when that has been bifurcated to individual
I mean name, then what is that as a builder
I am conveying, I am already given the
I mean to be.
So there is no land and no land only to convey to you.
Sir, I will not be conveyed to the individuals
first of all.
It is the sale deed.
No, it is not conveyed to me.
I will just you know put a barricade there
and answer it is my land.
Yeah.
Yeah.
So the common areas, whatever I am saying
that cannot be conveyed to the individuals.
Can you deny it?
Can you deny it?
Can't use that as their income and do something.
No.
I will tell you.
There is something called development plan
which is called DP.
In DP if it shows Godres 24 as a one single DP
and I think sometimes I will give an example
someone in the electricity and did the whole and entered.
So that will happen when they have a relink
with the DP with other products.
So now this Godres 24 has a sold DP.
Manetha is one more project, one more project.
Yeah.
This both cannot relinquish and have an interconnection
with those that kind of stuff.
Sir, one simple question.
One simple question.
This is not Godres' land.
This is like an helping with Manetha.
So who owns the entire land before Godres came there?
Manetha.
So it is all their land.
Tomorrow what will come next door we don't know.
And this Khatha is in their name.
This Khatha is the, see only your individual fight.
Which Khatha sir, that is what.
The project E Khatha is in Manetha's name.
We have that document.
It took that government point of view.
Why should that be their name?
We are speaking association.
It has to be conveyed to the association.
I will do one thing.
So give you a better understanding.
I share the details.
Recently one of the LASNA project in HEPA Road.
Poorva also had the same question.
So RERA has ordered LNP to transfer the common area in the name of association.
That is clearly there though.
I will share the details in both ways.
Because these are the recent changes in the last couple of years.
Which needs to be done.
Otherwise what will happen?
This common area will be still.
The land will be in the name of Manetha.
We are not saying that they will do something.
But chances are that they may do something.
So this common lecture about swimming pool and all.
UDS part I understand.
That is committee picture.
When you do redevelopment after 40-50 years.
That's it.
It will remain the same based on the trials and everything.
This kind of criminal activities will happen.
If I have consumed entire FR and FSI in the project.
When there is a small parcel near the CA area left.
Where I still have FSI to build.
Then this guy will, Manetha will after Godrej ekrit.
Then he will come until.
I will have the red shed.
I will have the shed.
I will sell it to someone.
Then if you question him saying that why are you doing this.
Then he will come nearer to my name.
But in this project I don't have any such thing to do.
It is entirely consumed and it is all big.
No.
So the entire conversation is what if.
See you don't know you have to be honest.
No.
No.
You have to accept it.
If the complex needs to change.
How does redevelopment happen sir?
They are building the pure.
They have residential plot.
Plotting coming up.
Already the work has started.
I mean the one who is coming behind your marketing office.
Tomorrow if they want to dump something within Godrej 24.
From there so that it is feasible for them to carry their load.
I am just giving an example.
See we have not seen future.
They don't know what will happen tomorrow.
4 acres.
Right.
If they combine their CA lakhs.
Together and say we have 24 acres.
Please what happened?
He cannot do that.
No.
What is it?
Because this is a separate DP.
This is a separate entity.
Sir just to add there is a pretty shared class of it.
Yeah.
And also that.
The cricket area is there.
The small piece land belongs to Manekha.
What if tomorrow as you said.
Join back.
They may ask us to do that.
We are not saying they will do that.
But that is a risk that we are carrying.
The land has to come.
And that should be transferred also sir.
What is the picture?
So that convoying thing has recently come up now.
No sir.
This is before.
Yes sir.
We have come alive.
It is all came after Vaira.
Okay.
It is all came after Vaira.
And people have started to introduce that.
Even the competent authority also came recently.
So what we are saying is.
Though it has come up now.
And we are still at a verge of taking handover.
Still your registrations are happening.
And still there are flags which have not been registered yet.
Can we do this right now.
Instead of you know pushing it to future.
And making it more difficult.
So check with your legal team.
And start the process.
I have already checked.
So what are they saying.
All these while we have suffered earlier.
Without this tool only.
If it is applicable also.
We will not let that portion to do.
Because we have already have.
There is nothing to convey.
We have already loaded this into customers.
So what if we register.
What if we register under cooperative societies act.
What if?
Register under cooperative societies act.
Who is the competent authority.
Registrar of cooperative society.
Correct.
That is what our DOD also says.
Correct.
Currently we have not registered our association.
Correct?
Correct.
It is.
It has been registered.
The DOD has been registered in the sub-register office.
We have intimated the competent authority.
That this is the DOD.
What if we do it under cooperative societies act.
The land has to be conveyed.
There is provision for the land to convey.
Provision yes.
There is a provision to convey.
Which we need.
Right?
We need to do that.
Otherwise we can't do handover.
We can pledge this land.
Because it has happened in Bangalore.
In Bangalore.
17 years people have fought with this.
We don't intend to fight with you.
There is one more way.
There is one more way.
Which I think if everybody all the owners considers.
Now that you are saying this.
That no it won't happen.
And there is an assurance from Manita also.
And it's all covered area for Godrej.
Dedicated only for Godrej 24.
We all buy that only because you are saying right now.
But to prove it.
To make it a solid evidence.
Even for the future right.
Will you be okay to get a legal letter from Manita.
Stating clearly that yes.
This property is solely for Godrej 24.
Dedicated.
And even in future we are not going to.
You know get into this property at any cost.
Okay I will definitely.
No Manita.
In that.
No no.
I am asking from Manita.
Legal.
From Manita's letter head.
From their management.
No no.
See legally it will work.
It's coming from Manita management on their letter head.
With a stamp.
With their some senior director signature.
That is also legal.
That will have to be registered again.
Sorry.
That will have to be a registered document.
Registered document.
Registered entity.
No absolutely.
I am not denying it.
Eventually.
So proceeds any other letter that we take from Manita.
Absolutely.
Absolutely.
But what I am saying is.
Since he is also saying that the new rule has been.
Has come up just now.
It did not exist in the past.
And still all the properties have been there.
He says there is a provision to get it conveyed to us.
Yes.
Let us do that.
Simple.
Simple.
What is that provision?
What is that provision?
What is that provision?
What is that provision?
So what is that provision?
What is that provision?
Because that means there is a chance to do that.
But how?
That is what I am asking.
You have to.
I mean through which?
Through which?
Some.
Some.
So one example.
You are saying that let's get a letter from Manita.
They will not do anything there.
Correct.
Any construction or anything.
Correct.
If Manita do a mortgage.
Okay.
And Manita goes to a bankrupt.
Another scenario.
Okay.
So they are saying that they will not construct anything.
But they are already bankrupt and this land belongs to them.
By default legally we will be liable as the land belongs to them.
Right.
So there are many angles.
Okay.
One letter doesn't work here.
Always the best solution is to get it under us.
Okay.
Through a condensate.
So that it is permanently resolved.
One we will go for one letter, another letter, third letter.
It will be a lot of complication it creates.
But see I will tell you everything.
But also there is a clause.
Right.
For example drainage.
Drainage is also written on the same letter.
Tomorrow Godreji will go.
But if there is a way.
That should suffice.
That way through they have different approach.
Cooperative housing society.
That we are not agreeing with.
It's registered.
If it register under this only it will not happen.
Usually builder doesn't do this.
But this is for us.
It is not a script.
If you don't do it you can still continue to survive.
But there is no harm in doing.
And we want that to happen.
So why can't association take this possible?
Sir.
Start conveying it.
Why would that be?
You are the one who found the LLP with money.
It is not necessary.
I mean I did whatever the right thing to do.
I mean.
It is not the right thing.
It is not the right thing.
The ethical basis is not the right thing.
Tomorrow there might be one more deal saying that.
Sir.
It is also you have to do.
Sir.
One more.
The culture of flats in Bangalore is not very long ago.
Whereas every other metropolitan city registers it under the
cooperative society's act.
Housing society's act.
Correct?
Not.
Okay.
The main ones.
Because what happens is complications come later.
Not today.
Today we will all be happy.
We will be enjoying the property.
After some time we will have challenges.
At that time we will have to go at the mercy of any other.
Something happens tomorrow.
Who knows, right?
Natural calamity happens.
The whole building comes down.
Who will we go after?
Will we be able to take that action?
No.
Association does not have any rights.
So can you check on this and get back to us?
I will let Prasad come.
We will speak to him.
No.
I don't think we will be able to wait there.
Because even I need to leave.
I have got a meeting at 2 so I need to leave in the next 10 minutes.
It will take 30 minutes.
I am not going.
I am not going.
One more thing.
Again this might be trivial.
Mr. Shaji's heater was opened after 3 months.
This much of salt deposit was there.
The treatment of STP, we are paying huge through our nose.
WTP.
The treatment of it is not being carried out at all.
We are paying so much to that vendor.
It is not my case.
Many of the appliances have gone bad in the last 3-6 months.
The life of this thing I am talking about.
That is one part.
The quality of the water.
Skin diseases, all of these issues.
Secondly, we are saying Bescom has an issue.
If Bescom has an issue, we are going to DG.
DG costs have gone up.
Bescom prices have also gone up.
How is that going together?
Bescom.
You get what I am saying.
Bescom.
DG stands there.
Time from day one, we are switching on the lights.
Whatever is there.
Lights are never turned on the other day.
We have to tell them.
Why are we keeping these FM people?
Praveen, that is what he said.
Take a approval.
Because they are not listening to us.
After 2 or 5 months he likes our stuff.
Before paying the bill, take our approvals.
They are not doing it.
Because we found that is only the last reason.
So the thing here is Bescom prices have gone up.
And our DG costs are going up.
See once this government after this change,
they have revised the taxes.
Half the time, power is not there.
Once the time, power is not there.
No, no, no.
Who is responsible for all that?
We can't be unnecessarily paying for lifetime.
Is it a fair move?
You tell us.
There is a comment from Bescom.
They are asking for the bill.
To this point?
Yes, Mr. Hemant and this one, this Bescom bill.
We need that one to be transferred to Godhe's 24th name.
I think it's on the month.
It's not there.
Because our GST actually is hanging.
I have already given the NOC to Rani.
No, they are not considering the NOC.
Just now we have received data.
For the GST, they are saying the Bescom bill has to be on the Godhe's 24th name.
So we just now received the notification from GST department.
Bescom name transfer, we required NOC.
I have given it to Rani.
It's already given.
But who will do that one?
Association.
Sir, it can connect to the local.
Sir, where is the NOC?
Rani.
He gave the hard copies.
When did you give that?
When?
6-7 months back, I have given it to them.
An association on the telephone.
In the month of July.
So, who did you give to Rani?
I gave it to him.
So, he just gave it to him?
He gave it to him.
She is having it?
She still has it?
Another point was...
She is still having the document?
Then we will see.
We can ask her.
Till the drainage is done.
Okay, okay.
Can you show that one second?
Just want to be sure that we have at least 5 points.
I will take it.
I will take the NOC today.
If we don't do it in 7 days, you will have to give it to IHT.
Let's do that.
We will have to catch him.
Who is he?
Call him.
Sir.
Sir.
Do you want to check the NOC once?
That they got it?
Yes.
So, we will have to transfer the NOC in the mail, right?
We don't have time for that.
No, we will have to give it to him.
We will have to give it to him.
We will have to contact him.
Who was he?
Who was he?
He was our manager.
He was our manager.
He was our manager.
What is he?
What is he?
He is our manager.
Don't take it.
Give it to him.
Give it to him.
Can you give it again?
I will give it to him.
Call Rani and say if she has it.
Because 7 days of the time, as they will decline the gesture thing.
They will come again.
Not at all.
But they will come again.
They will come again.
What is the problem with the Frees thing?
Okay.
Rani, you must have forgotten before 6 months.
No, I mean he can also go to the misplace.
Obviously.
Okay.
There is something else.
Is there anything else?
Done.
Done.
Bro, we are talking about the tanker cost.
Where is the drainage cost?
We will have to talk to the tanker cost and Santosh Patel.
Obviously.
And you guys have to...
Please give drainage.
They should do it.
Which one?
Not the water tanker.
Oh, not the water tanker.
The drainage one.
They will take the cost of the water tanker.
Yes, they will take it.
The tanker is coming, right?
How much is the water tanker?
2.5 lakhs.
As of now, it is around 1.5 lakhs.
2 lakhs approximately.
What if 439 lakhs, some new double.
Just to add.
4.5 lakhs.
No, no, I think...
I think...
No, no, no.
Ravi, no, no, Pradeep, Pradeep.
I am talking about drainage tanker.
Extracting water.
That is what I am saying.
Currently, it is around 1.5 lakhs also.
Because around 5...
Now, you are charging very less.
Your vendor is now taking less.
No, no.
But we know later.
Once you...
Whatever points you have given me, like water tanker.
And one for...
Ideally, my management has rejected to date of tiller cost.
Whatever I have...
I was given a provision of absorbing.
I will also have to go back and justify saying these are all we have.
It is not easy.
Any corporate...
We understand.
It is not easy.
Anyone doesn't want...
We also know that there is always this buffer kept when you build a project like this.
Right?
It is not letting you...
You will have to...
Five by six are...
You will have some buffer.
Sir, the point is much simple.
We are with you.
You please be with us.
We know you have to fight it out.
But we want you to fight it out.
What is the valuation of this project?
Tell me how many crores?
How many crores?
How many crores?
You should know right?
How much?
500 crores?
No, no, no.
How many crores?
How many crores?
Tell me.
Wait, one second.
No, no.
We have sold it for 85-90 crores.
Okay.
That is the highest.
Tell him.
Tell him.
I don't know.
I am not good with numbers.
Sir, it's a...
But you know that number.
Just 250-300 crores.
300 crores is not a big deal.
It is not a big deal.
It is sold for 300 crores.
What are the 50 lakhs?
Owners are not happy eventually.
You need to understand that.
What percentage is it?
On a positive note.
Okay.
Once I got to Godrej,
I nominated my two more...
Two more months.
They also bought two houses.
Okay.
They will be kicking you now.
They will be kicking you now.
I am telling you.
It is a 50 lakhs.
It is not a huge amount.
It is not a huge amount.
Okay.
Let's look into constructively fixing all these issues.
We are getting a 400 happy customers.
Think about the potential you have.
Right?
Because still I believe as Murini was mentioning,
I went with the Godrej because of my Godrej law.
Godrej is this one.
That brand.
That brand.
That trust is getting diluted now.
Okay.
Or that trust is closing now.
So, we need to rebuild under Godrej's little constructively.
This 30, 40, 50 lakhs.
I believe Godrej is not a huge amount.
Absolutely.
And we can promote this here.
Because we are at the fairs.
We can install.
Yeah.
You can look at it.
I don't have any problem with this.
I don't have any problem with this.
Yeah.
I have no problem with this.
Currently, the rating is 0.4.
We are ensuring 50.5.
Your Bangal Lens that you are launching in Budi Gharay,
you check the rating.
We, for 39 hours,
will ensure it hits 5.5.
Yes.
We can ensure that.
No.
You tell us.
Otherwise, we will have to protest.
You will see.
In that, your starting price is 1.9 crore.
That's why I am saying that.
I am going to channel partners.
I am going to do this.
You will be spending some amount of money for Google.
Yeah.
For free.
Yeah.
For free.
You want to use your own movie style in Budi Gharay.
We will tell to three people.
The same.
Please understand the sentiments.
People are...
Please understand the sentiments that we have.
Whatever you said,
one has much heard about it.
Please get back to us tomorrow.
Please get back to us tomorrow by 3 pm latest
so that we have clear, definite answers from you.
We will publish it to all the owners.
And of course, if possible,
please send an event to all the owners.
Including the association.
So that everybody has...
Sir, our first request was to create an owner's DL.
And the owner's DL.
Distribution.
Distribution because of all the owners.
Like, we have an association DL.
Owner's DL.
That was our first demand.
Okay.
I will put.
Because what is happening now,
we are not getting the complete details.
When we ask someone, they say,
it's restricted, we can't read.
One DL will be easy to communicate.
Adding all the owners to one distribution here
so that you send an email, everybody gets it.
See, it's their problem.
Whatever you do, all the way requesting,
send it to all the owners.
Send it to all the owners.
I mean, whatever update you have on this meeting,
it should go to all the owners in the box first hand.
Not from association, not from any of us.
It should directly go from Baudrette.
That these are the points discussed.
This is Baudrette's decision.
And we will stick to this.
By tomorrow, 3 pm, please.
Not also.
Not to all the owners.
You already have all the details.
You just need to know anyways.
Why should I?
It's all the owners.
What's wrong with that?
It's all...
You will have all the owners.
How will that help?
That will help because everybody will have
insight on what is coming from Baudrette.
Baudrette is the owner of the house.
Who paid you?
Who made the payment to you?
I know, I know.
That will create...
You are liable to answer that, sir.
That's all.
I am aware of that.
You have written to me.
I mean...
Honestly, if you have written to us.
Fine, you send it to us.
We will share the same thread to the owners.
But we need it by tomorrow 3 pm.
Today only you send what else?
Fine, send it today.
No, no, but...
No, no.
No, no, no.
No, no, no.
No, no, no.
The resolution.
No, no, no.
The resolution.
The resolution.
Just...
The owners deal created immediately.
Owners deal, it's up to them.
No, no.
We have to pay...
Don't be...
We want a solution.
We want a...
Yeah, that's what you are saying.
We need a solution.
No, no.
We need a solution.
We need a solution.
Yeah, I mean...
Whatever we have to come back is on...
GPL, absorbing the cost.
C.
I am telling you.
I am personally okay if all are okay.
I don't even need meeting minutes at the moment.
All I need is a final solution and decision.
You take time till tomorrow.
Give us okay.
Godrej, this was discussed.
This is our solution.
This is what we are providing.
We are ready to absorb 50 lakh cost.
Done.
We are ready to give you document with accountability for...
We are ready for this.
We are ready for this.
We are not going to do the...
12 months.
You will have to be sure for two more months.
Give us a final letter.
We don't need meeting minutes.
Give us a final letter.
Take time till tomorrow morning, afternoon.
But give us a final letter with proper solution.
Otherwise, two months later...
Which we can...
No security, no water, no this thing.
That we don't want.
Yeah.
What are the consequences?
Once you fulfil, we will go back to owners.
We will conduct a GPL.
If we get majority voting, we will proceed with handover.
That's an assurance.
After photo.
Conditional voting.
Yes.
Photo is a part of that list.
So of course...
We will do it.
Then how is this...
I mean, absorbing one to three points helping.
It's just like me going back and checking again.
No, this is...
This is again...
So what I am saying is, your tomorrow's mail or today's mail...
Will help us get a clarity if we are okay with it.
Or if we need to take further next steps.
If you agree to our terms and if you give us a proper solution...
Yes.
We don't need to worry.
We are okay with it.
We are okay with it.
You are getting my point.
So everything is based on your response.
So if your response is favourable, we can think about proceeding with it...
With the consent of all the owners.
If your response itself is not favourable, then we will see how we need to go ahead with it.
Okay.
My next point, if I am going to GPL...
Yeah.
If they agree to...
Hmm.
If they agree to extend their support and maintain it for next two months.
Hmm.
Can I commit them that you will be giving the...
I mean...
Provided they give the appropriate competitive rates.
Competitive rates and also we need better services.
Because there has been a lack of...
Yeah.
We have seen that they are not...
They say they will have fair chance.
It's not a confirmed thing.
Yes.
So they have a fair chance.
They have a fair chance.
That's it.
Otherwise they will have fair chance.
So they have a fair chance.
They can't sell that because...
Yeah.
No, so...
Otherwise they will have a fair chance.
Otherwise they will have a fair chance.
Right now they have no chance.
They have absolutely no chance.
Because they have no chance at this point.
But you can use this for convincing for your negotiations.
Yes.
Definitely.
See, you can't have...
You can't employ a CEO and then...
Managers under it and then associates...
To do a foreign property, correct?
You need one escape manager who can run the shop.
No, fine.
To answer your question, yes.
There is a chance.
If they give a competitive pricing, quality improvement...
And if they are willing to really do it in a better way...
Definitely.
I mean, if I'm getting a GLP and doing a better services for the same price that I'm getting from other vendors...
Even I...
What's wrong?
I mean, I'm happy with it.
Can you stick to it?
Yeah.
But they have to swear...
But they are giving him a price.
Exactly.
Let me tell you.
I have...
Like, we have had multiple calls.
No purchase on the price.
Thirty-three thousand for a security.
Thirty?
Thirty-three thousand, initially.
Now we have reduced it.
Yeah.
Who will pay thirty-three thousand?
That will be negotiated.
That's what I'm saying.
Your team would have done it with GLP.
Ninety-thousand?
Yeah, you said thirty-three thousand.
You will get ten percent.
GLP at ten percent.
Sir.
Sir.
No.
Sir, it is said that thirty-three thousand they are taking from...
But they are making ten thousand by the right person.
And the manager is getting somewhere sixteen-seven days.
So what is happening?
No one knows.
I know there will be some charges for you to the service provider.
Just to repeat.
Thirty-three thousand they are taking.
What does that mean?
Thirty-three thousand.
One is getting sixty-seven days.
Super-wise.
So it means a hundred percent margin, right?
It's almost, yeah.
So they are not paying thirty-three.
To the actual employer.
No, you are not paying.
Mr. Hemant, I think you should be knowing it.
Yeah.
Yeah.
GLP is a separate company.
We have...
Yeah.
No, no, no.
We are not saying GLP will, you know, you know all the...
Insignal as a story.
Insignal as a story.
Let me be very clear on this.
Earlier, before GLP comes, we used to manage with CBR.
I have full control.
Without my signature, CBR will not sign entity any contract.
I had full control.
Okay.
GLP is a separate.
It's like fighting over me.
I mean, it's like pure enemies only.
We and GLP and directors sit together and whatever you told,
I take the interest and blast them.
So we are in that house.
We cannot go and sit in their car seat and they show me,
Hemant, what is it?
That would be lovely.
Fine, we understand.
So have a conversation and get this done by tomorrow.
This is a huge difference.
Thirty-three thousand taking and giving only seventeen thousand.
And they are literally crying.
If you really have to analyze everything,
I think not just two months.
They should be in a position to run it for another two months.
I mean, four months.
The way they have done all this,
Just to add up, some security guards,
even they are doing a cook job or part-time job
within our society to un-let their livelihood.
If they are doing a cook job,
there was one security who left and he became cook.
One was a tanker driver.
He has left the security job, he has become tanker driver.
No, he is running tanker.
Inside.
Inside security.
They are actually coming and dropping this water tankers inside.
We know those security guards.
But anyway, that's a separate story.
Let's wrap it up.
Parasad is coming.
What is gonna happen?
Is he gonna take time?
Take time.
There is nothing different.
It's the same thing.
No, it's not possible.
It's not possible.
No, it's not possible.
Sir, sir, please.
No, no, we don't want it.
Add it to mental health fund.
Add it to mental health fund.
Already depleted.
Thank you.
