So, I have prepared that one two three right. So, let us go to the first one which is the
main excavation thing for us which is two months thing right. So, we really we should
not be asked to pay anything before every life that is very clear. See if you have not
another thing I will tell you before you answer my question. The apartments which are not
registered also you cannot put that difference amount on us ok. You have to take that in
your bucket later on you recover it from the people who are going to register later on
do not ask us to pay because we are not going to. The people who have registered are not
going to do that. So, I want your answer on that one first.
This is really to be a two months shortfall that they have created.
And the other thing is you know we were because the contracts were signed with GLPL right.
We were not able to do any negotiations right. So, we were not in a position any time during
midway where we could do negotiation reduce the price. Because you had signed all the
contracts for first 12 months which means you should have a clear projection on how
you are going to run the society for 12 months. And if I may add.
No other questions on that please. There was she if I may add there.
Yeah. We were not even given original receipts right from the day we have been asking.
Yes.
During the life we have been asking there is no deal business deal that happens without
a receipt being provided if I am paying for it. If I am paying for my services I need to
know where I am paying. Yeah. And if you are paying.
There is one side of GLPL keep saying that there is already been given to the association
that is the deal that is going on. Yeah.
And you guys are planning. Association go talk to the association you talk to the association.
We have emails starting from June where we have been asking when Rani aunty was there
everybody was there. We have been writing emails to you guys.
They said that there is an email where you have written that you take financial handover
we will give you receipts. We will give you the complete calculation.
Okay. I have that. Okay.
Okay. So we don't want to get into a conversation.
So this meeting is called because I wanted owners and association to be on same place.
Okay. And it is a very difficult task.
We also want to move on. We want to move on.
We can't be in this deadlock situation. Yeah.
So you are trying to create a situation in which emails when it comes from owners
you are saying association has been shared. Okay.
That that's not fair. Right? You are passing the vote.
We have an association. When we have an association we attack to Junaid.
Because we don't have an answer. Right?
Junaid is very clearly decided that he will not talk to any of the owners.
He is very clearly ignored us. Yeah.
If you have to do that you have to keep us also updated. Right?
You cannot keep us on the midway. Okay.
And then you can… So we will… I think what you…
Your first question is regarding one year of maintenance. Yes.
Okay. So see if you look at the agreement to sale.
Okay. Agreement to sale. And you know if you look at the registered sale date.
Okay. It is clearly mentioned.
Agreement to sale if you see. Actuals.
It is mentioned as estimate amount. Yeah.
Estimate. Okay. Right.
Come to sale date. It's clearly said that your spend will be on actuals.
Any difference shall be billed and collected.
Proportionately it will be billed and collected. Yeah.
So can you pause it? Okay.
Can I pause it? Okay. What is the last plan you said?
Billed and collected. Actuals. Actuals.
So from June you started billing if I am not wrong. No, May.
May second. May second. It will be…
June 1st you might have decided the invoice. Right?
Correct. Correct? Yes.
So June 1st invoice.
June 1st invoice. August 1st invoice. Where are they? When it was shared.
And if there is a difference in charging expected and if it is overshooting,
why you didn't inform to association or owners in the Q1 itself?
Assume there are 4 quarters. Yeah.
Q1 itself you got to know that there is a suit up to be maintained in the property.
Why it was not conveyed? Here they took them to us.
There is a suit up. It's not all of a sudden in October, November,
everyone increased their charging rate. No, right?
You started paying the same amount from June 1st.
For May, June 1st is the invoice.
And I got to know that from all the invasions are in the PDF format.
But whatever you are sharing with association.
Exception. Exception.
Which is coming for us. Exception. Yeah.
Which can be manipulated at any point of time.
And that is a shared thing.
Anything. So the question is JLP is raising the invasions
and those are in PDF format from June onwards.
But you never shared with association or owners.
And there has to be a minimum responsibility when you are running it for the first year.
To make sure that we are aware of what is, where is it being spent, how can we control it.
It's not like we have given you the right to spend it like how you please.
I remember. We have, it is hard on money. We have paid it.
I have had conversations with you while paying it.
Is it 3 rupees? You said it's on the higher side Praveen.
It is on the higher side. It is with the buffer. Where has that buffer gone?
And we have multiple times.
And now sitting 8 month, 9 month saying it is dry.
Is sheer, you know, no responsibility at all from the builder side.
And we hear when we ask about the bills or details.
It seems you have been communicating to the association.
As GPN is supporting money, we have complete right to spend.
You take the hand out, then only we will give the details.
I mean, in detail where it is spent, how it is spent.
So, while there is so much delay, after 8 months you are saying 9 month I am running out.
You should have told in the month of June, July, August.
We met first in the month. Do you remember?
Yeah.
September we met. October we met.
Did you ever open your mouth?
All the contracts were signed.
Ideally one mail from GPN should have been done in the month of June when association was formed.
July, August. August we again had a meeting with you guys.
You should have written one email to us.
Us in the sense association as well as owners stating that it is going higher than what was budgeted.
We would like to sit with you and figure out where we can reduce so that we can meet the ends.
And October when we asked GPN also, they had said we are well within the burn rate.
That is planned.
Yes.
Where did that burn rate go now?
No.
It went out of the window.
When we sent an email in which they said that on an average it was always below 3.5.
Hey you sir, are you coming from your side sir?
Yeah, please.
First thing I know is the calculation.
Okay, let's have a look.
You can talk early or anything additional to this that we got.
Association.
You do more than enough.
No, financial.
You were there.
Dinesh.
You were there.
Have you received anything?
You were asking.
I am asking.
Every society has monthly expenses.
Nothing was shared.
So we were always told to take handover.
Why handover is left to the monthly city.
In every society there is monthly expenses.
Whatever it is.
One by one.
Okay.
One by one.
Sir, please.
One more thing.
Projections for the dwellers.
How many projects have gone wrong within 8 months?
Approximate?
No.
No.
No.
The first time.
Yes.
Yes sir.
I think that's the reason I think we don't get more crowd if we don't do product.
Let's go by point by point.
As you can see, any of the society, 3 rupees collected, it is not promised that we will
maintain performance.
If there will be price appreciation, there will be price decisions, there will be wonder
scene, there will be multiple factors.
None of the project builder will take that maintenance and run the flow.
It will always be built to customers because we as a developer are into development.
We are not into facility management.
We are up for facility management companies.
We had our P\&L on revenue of green.
So this is not sufficient.
We will have to reverse to 4.5 and then run this.
Sir, you just offer interest.
Wait, can I?
Wait, let me say.
I heard you.
I have a response after you.
Praveen, I spoke to JLPL's leadership yesterday.
What they are saying is that Godrej does this every time.
3 rupees they tell because they want to keep the unit rate.
When people are buying, they will see the end amount to keep it low.
That is a part of sales strategy.
That is a sales strategy for you.
Who has read the comment?
They are interested in this.
Can you complete your statement?
No, okay.
No, okay.
Why are you asking me?
Why are you asking me?
They are not right.
They are still not super fine.
We will continue.
Usually how builders operate.
Once maintenance is exhausted, they will go and touch the car bus.
Sir, we know that this part.
Let's move on.
So we have not touched it.
All this, who has come, the ones that Cams has done,
they have been motivated that we will not be taking any more questions.
Right.
I have a question.
You are saying that you have not touched the car bus fund, right?
I remember a mail from Junaid.
No, but that is the unregistered flats.
They are not paying for it.
No, no, no.
The maintenance fund was something around 2.4,
but the car bus fund came down to 1.9.
No, that is because the unregistered flats have not included it.
That's all.
That's a different thing.
Let me come to one thing.
Let us also know that you said you are not in the facility management space
or the housekeeping space.
You are.
You probably, Godrej, properties is not in.
GNPL is the one whom you entered into a compromise
to maintain the housekeeping for us, the FF for us.
So for us, Godrej is one brand.
You should understand that, right?
Why have we taken an apartment with Godrej?
Because there is a certain level of trust.
Now that trust is being questioned.
That fundamental trust is being questioned
when you are saying one thing and doing something else.
Where did the 125 years of experience of yours go
when you said 3 rupees to us?
It is not like you said this 10 years back.
You said this one in the beginning of the year.
5.
4.5.
Have you heard that for a 4-inch property for 439 flats
for a building like ours?
At that time you say, when you say you say it's premium,
but when it is coming to maintenance,
you say it's not premium.
You have seen the pool that we have.
If 5 families come into the pool, the water is outside.
So let us not talk about what is the level of eminence.
It is not premium.
It is not premium.
How will you justify 4.5 rupees being spent?
For a non-premier.
It is 1 to 4.6.
See, October, November, December it has gone.
If individual, once you see it has gone about 4.
I mean, there are laptops being purchased for 2 lakhs.
Salaries of FM managers are 1.8 lakhs.
Salary for the month?
No, no.
The facility manager or the estate manager who is there,
there are 2 of them.
There are 3 staff members.
It is 1.8 lakhs.
Why did we assume that there will be 3 people to manage their property?
The cost incurred by us, by the association.
I have heard the laptop of Tula.
I will tell you how he is coming to 2 lakh rupees.
It is around 3 to 4 thousand rupees per laptop.
If you depreciate it over 5 years, it will come to 2 lakhs.
That was one of the points which I raised to GLPL when,
in the month of November starting, we received no email replies from them.
No email replies.
They were like, we have agreed to GPL.
You come to me, face to face, I will reply.
I was like, why?
You have to write it on email.
I will never go that way.
See, we will work with you to reduce the cost.
You know where the higher costs are.
There are inflatable, inflated costs that we have created to the vendors.
And the first thing we understand, that is how it works.
This is not the first time we are getting into a deal with the builder.
Many of us have bought flats in other ways.
What we want to do is, both of us should behave differently
than some of the other Agrade builders that they compete with.
See, already there is a, let me complete this.
Already there is an impact on the brand goad race in the south.
Whether you accept that or not, I don't know.
We spoke to Akua.
Akua also, you had the same thing go there.
Let me complete this.
Let me complete this.
No, I am not complaining.
I am not comparing.
I am talking about the brand goad race.
That's all.
I am not comparing.
That's why it's different.
We are different.
But the same thing unfolded there.
Elections were conducted in a questionable manner.
Let's not get there.
That's a different conversation.
We have been fighting internally just how it has been scripted
by whoever wants to do that.
Now, that script has been running.
People have been busy doing that.
Why you have been not addressing the real issues that we have handled?
Lift has been an issue that we have raised.
Initially, it was a maintenance thing.
I myself got stuck.
He himself has gotten stuck in the lift.
And he said, I was scared to death when the lift stopped suddenly.
He said that and suddenly he goes back.
In one hour, he goes back and writes a completely different email.
I mean, is that something that you want to stand for from a customer service standpoint?
It's a question that goad race should do.
What do you think?
It's a maintenance thing.
I will add one more point.
One second.
We are diverting.
We need an answer.
I have one more point to make on security.
Let's hear from them.
Let's hear from them because we will continue our conversation.
One more point on security was a factual point.
We evaluated four security agencies and we could get in no time,
in two weeks of time, we could get lesser price,
even from a better security agency than NSEC.
When we shared it with GLPL, they reduced that price.
Why did you keep it at the highest level possible with NSEC
and keeping GLPL's margin, your margin?
And now you were saying that it is too much of deficit.
It's not acceptable, right?
You have done your job, no.
So see, when you are promising at the time of sale,
you should be doing your job properly.
You should be doing a contract in a way that the money is sufficient for 12 months,
not closing your eyes and giving the highest price whichever is coming.
This is not the way to manage.
And we are saying to you because you had the funds.
You were managing, you were paying it every month or month.
And when I told Juner that if the fund is finishing, what will happen?
Sumit was also asking him, what will happen when the funds get over?
He is like, it is up to you. The DG will get disconnected,
water will not come, mescom will not be paid.
Is this the answer you should give?
12 months you should run without any question, right?
Are you telling that, no, tell me.
Are you telling at the time of sale that we will not run for 12 months?
No, right?
Sir, we did answer.
Sir, why?
Honour before August?
Yes.
Junai 30th, didn't write that why he is not shooting.
I agree.
Why we are not shooting?
When we were able to get from the market.
Sir, let them shoot.
The question is, he, 3 rupees, I agree.
It is not a fixed component.
There will be a little variation.
Yes.
Because the 5 years story we know.
Yes.
So the question is, when it is shooting up, you know in the month of June,
you know in the month of July.
Yes.
At least if you are calculated on a quarterly basis,
by August, Junai RGLP, whoever is voting that one,
should have intimated associates, all owners,
who are together to all the 439 owners,
that this, we are shooting up, we need to adjust somehow.
And we need to come and discuss where can we reduce the
Yeah.
Exactly.
Expectation.
Now you tell us.
We have with association.
No, we need to answer.
Sir, sir, we need to answer for this.
See, when we have the predictions,
all the contracts we have signed is a fixed contract.
Right?
With all the contractors.
And you signed before the apartment.
Yes.
So you had predictions available of how much funds
will go for how many months.
So if you would have raised and allowed early,
all of us together could have tried to cut down some expenses
and completed the 12 months.
Not at the end moment.
At the time of sale.
Okay.
I mean, you might have had a sale for one year.
Okay.
So I'll also tell you,
at the time of sale, you might have also asked,
what is the registration cost?
Did it, you know, be as per his commitment or did it shoot out?
That is a government team.
Don't miss it out.
Don't miss it out.
Nobody will buy that.
The decorum is not main thing.
The decorum is not main thing.
The decorum is not main thing.
It's not about decorum.
It's not about decorum.
It's not about decorum.
Wait, wait, wait.
One by one, please.
One by one, please.
One by one.
One by one.
I'm just asking you the best thing.
Registration cost,
registration cost,
is not variable.
I cannot negotiate with other veterans
and bring it down.
Registration cost is not that.
Please don't compare with registration costs.
Okay.
Here, we all met all the agencies
and we understood what is the break up
where we can reduce.
That means actually we can reduce.
First question is,
when did I share it with you?
Okay.
When was the first calculation shared to you?
Okay.
It was in the month of October
that we shared month-wise break up.
This is what is going up today.
Did you not share it?
Where did you share it?
It's the answer.
This is the...
No, no, no.
This is what I said.
That's a high average break up.
That is an excellent spreadsheet.
It says so much is spent.
What we are asking is the invoices.
How much did we spend?
The invoices are...
This, sir.
You can go on chicken,
how much did you spend?
That is not how you do, bro.
I should find a receipt
when I pay for something.
Correct?
Why are you asking?
My idea is that...
Sir, I mean, we have given invoices.
Sir, I mean...
Just give invoices.
Just give invoices.
Thank you.
Yeah.
Who did I pay the maintenance amount?
We...
For maintenance, we have paid the...
No, I have paid for you, right?
Yeah.
Now, is it not your responsibility
to provide us the bill?
You have given the invoice, no?
No.
How was it?
I don't know, how was it?
You see, a client here
were not hired by me
or not hired by me.
Okay, but...
Whatever...
After raising the maintenance invoice,
only you have paid for it.
So, there was one...
There was one...
Yeah, my amount is getting...
Just a minute.
I will answer.
My amount is getting spent.
Yeah.
Who is responsible
to let the owners
or provide details to the owner?
Sir, that's what...
We have a dedicated
face-to-face management company.
Okay.
Who is...
Correct.
We had also asked them...
They are coming to the GP.
They are coming to the GP.
They are coming to the GP.
They are also the GP.
They are in...
That's what I am saying,
they are playing ping-pong ball.
Yeah.
You know, putting us...
No, there was one e-mail...
No, there was one e-mail,
he was...
I can't...
I will say one thing.
There was one e-mail
which was sent to Junaid by me.
I asked him that...
In October,
I think in October or November,
maybe September also,
I don't remember exactly,
but maybe October mid.
I sent an e-mail asking,
now on, we want GPL to take
approvals from association
on whatever spend is being done
before paying to the vendors.
This was the e-mail
to which you replied
that, no, money is with us.
We will not take your approvals
until you take financial handover.
Okay.
We will not take financial handover
till 12 months.
Then do it, no?
That's what I mean.
One question, sorry.
That mail, whatever he says,
October to the Excel also,
does it...
There is a line saying that,
it is shooting...
We need to plan something.
Can you read it?
Is there any line?
Was there any code?
Any line?
It was an expensive statement.
No, that's all.
In your eyes,
how much we have spent.
No, I understand.
My question is,
was there any proactive approach taken
when it was known that it is shooting up?
Is it mentioned in any of the lines?
Mr. Rahman,
I mean, I'm sure you have heard
all the queries from the
owners and association, right?
Now, we need a solution.
We are here today,
as you said, for upon decisions on this.
We need your help
to extend the maintenance
for the next two months.
Because it's very difficult.
Please understand.
All the owners,
the way they have put their hard
on money for this maintenance, right?
It's not as...
As a company,
before I could come,
I've discussed with my...
Okay.
Management only, I'm here.
As a company,
we cannot bear the two months
maintenance.
During the association sign-off,
we can sit down table to table
and discuss how much
GPL can bear,
how much association can bear.
That's the response which...
No,
we are not discussing
all that sign-off.
That might be...
I mean, you understand,
but...
So, what is your leadership
saying on this?
I mean, understanding
the point that, you know,
we have saturated
the entire maintenance point,
at this point.
And we have another
two and a half months
still to go by, right?
So, how are you planning?
Because,
somewhere you...
I know that there was
a clause put across
in your sale date.
That's all fine.
But,
the kind of strategy
that you had during your sale,
everybody was put
their money into this.
What's your plan
to execute, at least,
in a way so that, you know,
we can cover these two months.
That's what I want to know from you.
See,
immediately I think
I mean,
association along with
owners, we are ready to
work on the cost-optimization.
We'll sit with you.
We'll see how we can
bring down the cost even if
needed.
But what I'm saying is,
we don't want to pay
even a single penny
to you,
at least till May.
We will, I mean,
not to us.
May second.
May answer.
Yeah, I mean,
after that,
we'll manage ourselves.
We won't.
But we don't want to,
none of the owners
want to pay even a single
rupee until May 1st.
That's the
head.
And that's why we are here
right now.
Forget about what has
happened.
Now we need a solution.
Yes, sir.
So can you,
I mean,
rough estimate per month,
how much it is?
So that's what I think
there was.
I understand.
So based on the current,
I think that's what was
projected 4.5, right?
4.5.
25 lakhs.
No,
no more than that.
No,
I think after GST,
it was 4.28.
See,
two months ago,
it would be 50 lakhs.
So,
somewhere around 50 lakhs.
It was earlier.
So you raise the invoice
to customers
and you can start spending.
Why,
why we will not do that though?
Why we will do that?
Then I think
we will have to compromise
on the services as well.
You should have called
out what would be the compromise.
You should have spoken to
the owners.
This is what everybody
says.
The service says
you cannot compromise on that.
You cannot,
you cannot stop
this one,
the swimming pool.
You cannot close
the clubhouse.
So immediately
stopping is different.
Service means for
security,
security,
security.
I think the
dignity is different.
We have
to have
one second.
Before this could,
I mean,
our legal team
has also put that out.
We'll be sending an email
to other customers today as well.
Saying that I mean,
this is the thing.
I mean,
we will have to compromise on the service.
I mean,
there will be
no one second,
this is the
contract you have signed
for one year or six months?
One year.
So,
if you have signed for one year,
how the rate is inflating?
Exactly.
We also signed for one year.
We also signed for one year.
We cannot
allow you to
remove the services.
So,
please tell me the areas
where the rate has inflated.
We have
passed the
sign for a fixed cost.
It is a variable cost.
It will vary.
So,
there was one more thing.
Julian,
if you remember,
I didn't discuss with you.
We also asked
Junaid and also
VNPL,
Chetan Bhaskar,
and even we had
meeting with Santosh Patil
a few days back.
We asked them to
really justify
on what basis
of the inflation
and all that is fine.
But we really wanted
to understand what
went wrong.
That the projection,
I mean, based on the
initial projection,
the actuals are so high.
That's
something which
may be
understood
exactly.
So,
we have not received
just,
for your
awareness,
we have not
received any
confirmation on that.
That what actually
was a major cost
because of which
the rates have
increased significantly.
And what is
the approach
right now?
Please understand.
It's,
now you are aware
of the situation
what has happened.
Again,
I don't want to
go into the past.
We cannot change it.
How things have been done.
We are here today
to get a solution from you.
As an owner,
we are here right now
to also collaborate
with Godrej,
GNPN,
to understand
how we can
ensure that
we don't have to
pay anything for
next two months
because we have already
spent so much
buying this
Godrej property
and paying the maintenance.
These two months
covered
within that maintenance.
So,
please help us
with this
and that's all.
So,
we can close
the number one
topic.
You've given
insurance till May,
May 1st.
That's it.
We will not be
paying any next
chance.
Sir,
first point
is just sticking
to the
sale rate.
Did you
give 15 days notice
to every owner
before
buying the
sale rate?
Yes.
Because the
S.P.L.
legally if you are going
you have to
share 15 days
at this
time
for the owner
to read
the
sale rate.
S.P.L.
DOD was not
at all.
DOD was never
attached to it.
Now,
not even a complete
DOD was there.
After
15th
August
when we had
owner's
Adam was
GPM,
there are also
many people
later we got to know
that it was
told by someone
to not share it
with you
but later
we got from
the DOD
S.P.L.
DOD was shared
to every owner.
I can
guarantee you that
even I got
just a day
before
the draft
of the sale rate
and
by that time
I was told
to
go to the K2
site
in general
it shows
the
duty,
pay the
credit for
7 days
only.
As soon as
they generate
there are
people who
are coming
they are not
allowed.
So
at this
15 days
notice we
have to
read through
the sale rate
if they have
any questions
come back
with the
questions
you could
have
complied with that
what happened
here is
we just
enforce that
whether you like it or not.
You are forcing
all the owners now
saying that
as per the sale rate
you can't tell that.
Second thing is
you are saying that
you are spending
4.7
as a
current
one rate
your one rate
has been
I am not getting
very
4.7
let me
let me
let me
update my
that is not
reflected within
our community
basically
one second
basically
there is
R.K. said
we need your help
to not pay anything
until the
end of the year
in the sense
until first of May
let us look at
what is possible
from yesterday
9
no
as per
as per
what was projected
I don't know
if you guys have
wanted more
as per
what we received last time
it should have been
till end of February
the maintenance
on May 5
till end of February
there was no
projection
that is what we
confirmed
there was no
projection
that is what
I am telling you
you have to know this
you can do better
so
so
we all
understand
there has been
huge disconnect
have taken the property, we have paid the maintenance, we are going through all of this, right?
There had been a lot of taxing things around within the society also, but at the end of the day,
I'll tell you, Junaid is also leaving, we are away. He has already resigned, he'll be leaving in few days
and I think most of them are also away. There's nothing to hide, but I'm just being very transparent.
Right now there is an opportunity for you, project is almost at a verge of if you guys do it in a proper way,
there is a possibility that we can also go for a handover if you meet all the clauses that we have.
Please, it's an opportunity for you to close this project on a right note, you know,
ensuring all owners are happy about it. Please don't get into a situation where, you know,
all of us feel that provided the photo audit happens, all of that completes,
and then we'll do the handover, there's no handover conversation before that.
We had enough time for that.
Sir, we have been asking how do we do the audit and we were told, no, no, you take it over,
we have done all the audits that are necessary. You are both rich, you have done all their audits,
but we are not satisfied with it. We have bought a property, we would want to do a third party audit, right?
There was no funding, best of all. You yourself are running shorter funds.
So these things will take time. You look at any new building that is taken over.
It is after 12 months that people have taken over. There has been a rush to take over from August,
which is also the reason why it was in a rushed manner, the association was formed.
People had opposed that. Please don't do it. We'll work with you.
To him, I had told him, we will work with you to sort out any issues,
but please don't form because none of us know each other. I don't know RK, RK doesn't know me.
Unnecessarily, why create an issue of friction within the 439 owners, right?
So the point here is, we were trying to do audits.
We also told him to delay you and we, you know, keep pulling you back.
You have other projects to take care of.
All we are asking is, give us fair amount of time to do the audits.
And for that, we might need to crowd source or whatever, right?
No, it's been a year.
Sir, 9 months.
9 months. I am still not shifted there, but still.
No, it is not a year, right? 9 months is over.
March onwards, let's say.
Let's say March 1 year, 7 months is almost done.
We don't want to delay it further. We have been talking about handover, legal audit,
I mean, an audit team, all of that right from August.
But for whatever reason, there has been a delay.
And I would be doubtful if there is no this thing from your side.
If you could also have facilitated, that would have helped.
Because instead, it was all diverted to have internal issues.
We have been fighting issues like, you know, the association is not legal.
Versus, you know, passing new rules and stuff like that.
We could have focused that on STP, best coordinated issues, lift-related issues.
And stuck to that, and you would have been at peace, we would have been at peace.
Currently, we are feeling it's a mistake that we did by coming and investing here.
Mr. Kamala already told us, you've got this at a good rate, now it is appreciated.
You should be happy that this is what you will get.
It's not the right statement.
It's not the right statement.
I have told that to Santosh as well, that's not right.
See, one thing which I want to mention, if the funds are adjusted, we put these funds...
Sir, we understand. We understand building properties as a very different business.
We are not saying...
There is a courtesy...
Just to correct my words, it's not...
There is a courtesy from your side, when you are an expert, we are novice.
To tell us, boss, you are money, you are in safe hands, but we are spending more than...
For any project, we form a body...
Sir, I understand.
I am not saying...
Just a minute. One of the projects, even if it exists, we never go back on the...
Even if it's a ten-hour project, even I go to our previous projects, if there is a legal issue, still I go on, sir.
First thing which we do is, we form a body and give the money, that doesn't mean that the biller is running away.
You guys always think, I mean, GKL is running away.
Sir, that is the state of the affairs.
That is the state of the affairs in the government.
That is your state.
No, no, no. It is a...
It is an experience.
It is an experience.
So, let's get back on the solution now. These are all side topics.
You give a solution because it's too much deficit or simple.
I have one more point. I have one more point to be added.
Okay, I am not sure you are aware.
We issue the PIL on 20th Feb.
In the PIL, it was clear to mention that on 18th day, the maintenance will start.
That is 10th of March.
Now, if you consider from that, March till Feb.
Oh, thank you.
Thank you.
No, no, no.
I think you gave a solution.
Sir, we don't return.
We don't return.
We don't return.
We don't return.
What?
What did you mention?
We have observed that...
We don't give a solution.
What is that?
Let's not go back into the past. Let's talk about the future, please.
We registered in Júttu.
We registered in Júttu.
We registered in Júttu.
It was the first period.
It was the first period.
It is clear from March till Feb.
It was the first day, right?
It was the first day.
It's not like that, it's not like that, 
We are sitting here right now, we are here for a solution, please understand. So, give us a solution on point number one, let's speak for other points and let's close this. As Junaid said, this is a final meeting with owners and association.
Okay, I can give you the number. So, fine.
So, I came from a management team.
So, what is your management saying that now?
See, we have estimate, it will cost 250 lakhs to maintain 2 months. Even if you optimize, I mean to the fullest level, you can bring it to 30 lakhs.
Okay. In the 30 lakhs, what can we wear, what can you wear, we can sit on the table and discuss when things are at peace and then taking over.
This is a final meeting.
No, things will be taken over.
Sir, I'm telling you, corpus, they have not touched.
Corpus, they have not touched.
I cannot.
One question, I have a doubt that they have also touched.
One question. You have 21 odd players that are unregistered. Where is that maintenance contribution?
They haven't paid to us and we haven't given to them.
Who has to pay until they are registered?
No.
No, they haven't.
As per the safety and DOV, it says that the lender has to wear the cost and you have to voting rights.
That is the case. You show me the clause. Where is it?
Yes, it's written.
It's written.
I can show you that clause.
It is right there. I have seen that.
When we are talking about safety, both the landers have to be paid until that is registered is what I said.
If it is really mentioned, I'll take it up for legal.
Yes, it is mentioned actually.
That itself is a good amount, right?
And you are saying 50 lakhs can come down to 30 lakhs. Why wasn't that legal?
That means we can optimize it.
Instead of insecurity, remove it and put it to 5.
Yes, we have to compromise on 50.
56 was before.
Everyone is not too comfortable with that.
No, sir.
Same reason.
No, sir.
The point is, the point was discrimination.
Sir, people are not proud of that.
People are used at the same time.
You are talking about the financial load going to come, how we spread it or something, right?
We already had a financial burden.
I will tell you one example.
We had enough lift issues, right?
Lot of concerns from owners and the man trap.
Everything was happening.
Because of that, the executive board has to decide to add a high security night.
Because we cannot keep people alive in a, you know, kind of a situation.
Like there was something happening, life threatening situation.
1.5 lakhs a month, okay, almost 6 months now.
I think we already spent some 9 or 10 lakhs already from the owner's pocket.
Because of the quantity of the service.
In your projection also, right?
And we are talking about 30 lakhs or 50 lakhs spending.
We are already running.
Similarly, the other example I am going to tell, okay.
Near us to 5 kilometers circle, I am here in a similar capacity of apartments.
Work they had, a builder has given a 5 to 10 bottle.
They builder has dictated.
And per day consumption is 2 lakhs, okay.
And the entire apartment, they are equal to satisfiable to the partner inside.
The builder has provided all those things.
Here it's like all we are pouring money, spending money from our pocket.
Where something coverage has not been currently.
That's what my guess.
No, we already spent a lot of money.
But no one will get the approval, sir.
I mean, let me be very clear and candid.
Even if you pay them under that table also, they are not in the position to give approval for approval.
Officially.
Unofficially, people are digging and they are taking the water.
That's the correction.
So, for his first point, sorry.
Where he was telling about the lift, he now he spent 9 lakhs.
This is because to save the GPL name, it was truly an idea from Mr. Duneil.
Sir, over the night, we put the security because of...
No GPM, nothing was happening.
So, there was a man trafficking incident in Tabari.
So, that is the reason over the night.
But before that, previously 2 months, we stayed without night security.
One at night, one at 4 security.
Just because of lift issue, to save themselves, especially Jureh and Gain,
they have appointed, they have taken association commission.
They took the allocated 5 security.
Each one, per month, it is 1.5 lakhs.
In the last 6 months, one has spent 9 lakhs for the mistake of GPL.
A second example.
Second example of it.
Is it not should be...
In the first place...
One second.
In the first place, he was telling me what he was projecting.
This society is somewhere which is very secluded.
And it doesn't have boundary or protection.
It's called, I don't know the security agency guy used some word,
which says that it is not protected on any side from any other building.
Okay?
In such a scenario, when you are giving handover to people who are coming first,
as a first resident, you were not putting their life in threat.
It was only 4 security.
Can you imagine this 439 flats, 6 acres.
You have projected only 4 security in night.
Really?
When you said it is 24-7...
Yeah, it was around 4 at night.
Right?
You said it is 24-7 everything.
Where was the security?
We already had incidents inside.
You did not predict there was security in Clubhouse?
We don't even know.
We even heard from GLPL that there were some people in the vendor employees
who were taking the chairs.
They were stealing the chairs from Clubhouse.
What do you have to say on this?
24-7, you only promised, right?
They were talking about incidents.
People were joking.
Yeah.
Talking about the expenses in recent years.
We had to fight for their friends also.
Because of a design or a consideration of competent authorities, STP,
now we have also started selling tankers out.
Now you always claim that the local body has not provided you the connection.
Having said that, you have no authority to leave the water outside.
You know that.
If there were villagers then they would have come and created an issue.
Today there is nobody who understands it, hence you are leaving it there.
But it is a health hazard.
Correct?
We all agree.
You will know.
The problem is, no consultation happened.
Now we are selling tankers.
Who should be wearing that costume?
Whose design is it?
Your design.
Why would we pay for that?
I didn't sign up for that, right?
Anything you say, okay, just because I bought it, it's jump in early.
I can't pay for it.
There are any other costs that I am incurring.
So it has to be a fair deal, correct?
And if you are sticking to say, we know that we need to pay money for STP water.
So we had a conversation also where we raised it to GLPL
that till the drainage is coming in the society,
you should be wearing the cost of tankers.
It takes 2 years, 5 years, 10 years.
We don't care.
That was straight away rejected.
Why?
There is no need to be somebody who adheres to all competency requirements.
You are the only one who does stale agreement, correct?
Brigade doesn't do.
Purva doesn't do.
So I am not comparing.
If you have such a thing, why not do it in every aspect of the building, right?
Why would you get pollution board certificate?
We say zero water to be sent outside the storm house.
Zero discharge.
Zero discharge.
But you are discharging it, saying that I have government authorised people to send this water.
Even if they come and catch tomorrow, I am authorised to...
Sir, who is going to pay for that?
See, ideally it should go in the drain.
It should go from the toilet.
That's a design problem, right?
It's a design problem.
See, I have designed my building.
I mean, I have an inklet about it.
Sir, now who has an ATR?
You tell me.
But again, it's a 439...
It's a major question on...
Don't you think it's a major question on your OC?
Because how did you receive OC without having a proper provision for water?
OC requirement is not for habitation.
They will see certain safety, fire movement.
They'll see the structure of the building and they give OC.
And after that, it becomes upon the maintenance.
OC is not a requirement for this.
Any project will discharge water.
I'm sure one project will...
No, discharging water is fine, I agree.
Every project, every property has it.
But if you don't make it a provision and if you leave it in a land...
Sir, at the end of the day, Godlet is a brand which is building homes for certain kind of people.
It should be livable, right?
It should not be paying a service.
So also I understand the point, right?
So as much as you guys have agreed to write it in a letter and clearly mention that you guys are accountable...
If any such KSPCV or any such inspection happens or even in future, you're going to make a provision for the training.
We should also.
Yeah, we should also, right?
Yeah, yeah.
So on this point, definitely we need that letter from you, first of all.
But secondly, I'm saying, forget about this aspect, right?
The other thing is, even if you discharge the water outside, as even Praveen said, from the health standpoint...
There is a water log which is happening in the adjacent land.
You know the situation right now.
There are chances that, you know, dengue, malaria, all these mosquitoes will start breeding and that's fine.
First point, let's conclude one by one.
So first point, I think he's going to check with his management and he's going to...
Why are you leaving it?
I have told you the solution also.
If you have two months' maintenance cost will not be put upon us.
What is that we are absorbing?
What is that you have to absorb?
What is that you have to absorb?
But how do you absorb it?
One bit first.
Why don't you go back to management and say that the...
Are you additional secretaries for the night time?
It is truly to save the GPL.
Do you think, I mean, management is unaware of that?
No, sir, you said...
You might say about it.
Sir, you always...
There are 19 to, I mean, 20 to 25 meals has been transplanted into management.
Do you think management is not at all...
Sir, then there's the issue.
And the response is also to the emails.
No, that...
The response is not satisfactory, sorry.
It's like saying today, start it by saying that you know you have signed your...
You can speak.
Sorry to say that we are getting a response from only from Junaid and who is in our notice period.
How to trust that response is...
And one more thing...
One more question.
We had many owners, you know, writing individual emails to you guys asking,
I paid 60,000 for example, I paid 60,000 rupees for 12 months maintenance.
What is the status of my 60,000 rupees?
Are you not liable to respond to it?
Money is with you, right?
You were half of the emails you wrote, association will respond.
How will association respond?
We told GLPL of no.
So this email was...
One second, this email was also sent to GLPL guys.
We told them to respond to that individual email, no response.
From GLPL?
Yeah.
That's when I told Junaid that stop their payment.
Stop their payment.
He did not do it and he's responding me keeping all of the Janta of GPL in loop
that we will not take approvals from you.
Why will we take approvals?
Then why are you coming now that it is a short of two months?
We will not accept it, right?
Why don't you do an internal enquiry?
What went wrong?
We actually have asked for that.
We have asked for it.
We will give a statement saying this is how we deal.
There's definitely some sort of a issue with the funding.
You give the expenses to them.
Like saying that it's more of an estimate collected.
And spend some money on it.
No, we will not come out of anything, right?
Even if you give expenses, what do we do with it?
Expense you can figure out.
Why should we come out of anything?
No, no.
Same as what I asked, I tell you, what I asked is there must have been certain projections
back then versus the actuals.
So I wanted a summary.
If Junaid remembers clearly and even Patil and Chetan and Bhaskar were there,
I told them clearly, you give us a summary.
I'm not looking for 20 pages of document.
You give me a 10 line pointer summary stating that okay,
these are the 10 reasons because of which the expenses have gone high,
justifying clearly and then let us review it.
And then we'll see, is it justifiable or if we have to take any action on it?
It's a light one point here.
When you see the first email in the month of October, okay?
So have you not got the details of the company?
They don't come to pass it on.
Sir, this is actual.
One sigh, one second.
You see this?
When he sent the mail on the month of October,
we along with the text of the organization...
This was the only mail which we got in October which we published.
I remember.
They did not send all this breakdown for every component.
We received one email back in October.
See, when it was asked that can we do the audits, can we start the bills?
You said that you sent us one final email.
We still have that email.
No, this was his wording, okay?
He said you sent us one final email where he would take the financial handover.
That's when he would share the bills.
Every time you would ask him.
No, did you not say?
Can you not tell me?
That you sent on the email.
We will share it only once.
We will share it only once.
Every time I can't go back to my CSN and prepare the room.
See, you don't have room.
You don't have room.
You don't have room.
You know what is that room?
You don't have room.
It's for you to tell you.
When you started the meeting, this is the last meeting.
How do you expect that this is the last meeting?
Tomorrow, if something goes wrong, we will not come back to you.
Who's saying that?
Who's saying that?
Who's saying that?
You say that this is the last meeting.
You say that this is the last time.
Fair point.
What do you expect?
We expect this is the last meeting.
Sir, even after a year, we will have the one more meeting.
Yes, sir.
Maybe it's the last meeting for Junete, since he also has this.
We are not here to fight this.
But this is the last meeting.
You will also be sitting.
It's not the last meeting.
It's the last meeting.
Let him find first, then we'll go ahead.
What happened?
Just take your time.
No, that was the same during September, October, 

Before that, May to October, you take it from security guys, no, extra 90,000, manage it.
This is not by reducing the headcount again, this is purely a negotiation that these people who were one month old in the job,
they could do, they could say 1 lakh rupees, you are industry leaders.
And guess what, within a span of one week, we brought...
With these guys only, and second all that, you give every project, 2-3 projects at least in a year, right?
Because it is your national partner.
Exactly. Mr. Hemant, within a span of one week.
We put it here, we don't care.
Within one week, we got 4 security agencies, sit on the table with us, we got a competitive pricing called NSAC, called GLPL.
We negotiated on the pricing for almost 90,000, it was reduced within a span of 7-10 days.
We did that as an association.
If they could do it, and that's why we struggled to understand that why GPL was not in a position to do all these negotiations right in advance,
knowing that you are projected only 3 rupees as your charges for the first time.
If it is 2 or 3 of us raising this, you can say that you are re-advised.
You come, first unbiased manner, you come in speed to every owner.
One owner who is reasonably satisfied with how the deal has been, show that person to us.
One person is enough. That means 439 people are upset,
and that 439 is going to talk to 4 people at least, each of them.
What are you going to do, right?
You also have a business model which is going to expand in Bangkok, Chennai and all that.
The word of mouth does it, this is the word of mouth business, correct?
If we are happy, we ensure that they did their part.
Godrej stood by what was supposed to be done.
Their customer service was better than many of the others.
Shobha, for example, doesn't give the common area, but we are not bothered about that.
We have come into a deal with Godrej.
We want you to give the common area to the association.
Godrej can't give us a gal about, you know, conveyance charges too high and all that.
UDS is another thing.
No, no, tomorrow, these are 40 years later, 40 years later, if my children want to get this,
what is the guarantee they will have it in their name?
What if redevelopment comes? I will have to go behind my name.
No, I will not have to, I have the time or the state to go behind it, right?
I am an individual owner who has dealt with you.
You have to make sure I am reasonably safe.
But the common area is already yours.
No, sir.
Okay, one more funny thing was there were few contracts which were like, what were those services?
What was that?
What is that? Pick up drop-off documents and all of that.
That was actually active film.
That was actually active film.
You projected that on the show.
Then I would say, imagine if you have that.
We don't have that.
So, one second, I will tell you.
Please understand one or two more things.
It was a projection.
It was somewhere around 3.5 lakhs that you projected for concert services.
Apart from that, there was also one, this Godrej ka app, living app.
Living app.
Living app.
That was somewhere around 2 lakhs, 1.5 or 2 lakhs, right?
We stopped immediately.
We stopped that also immediately.
Imagine all of these cost was included as a part of that 3 rupees.
I don't understand.
The service is like my games.
Which are the market leaders.
I give it for free.
You were costing 1.5.
Exactly.
That was my projection.
And moreover, right?
6 lakh rupees, he only calculated.
6 lakh rupees, they can do less.
So, why can't they do GPL?
It's the same sister company.
Exactly.
It was somewhere around.
It is somewhere around.
It is somewhere around, which pushes us from the back.
Take the financial, I don't need money in your head.
That's fair.
I think that's fair.
This is absolutely not professional.
See, we deal in professional companies.
We are working in professional companies.
But this kind of response and attitude is absolutely not fair.
I think they have given lots of points.
And he is agreeing.
Because you are also noting, that means you are also accepting this life.
It's not all that.
It's not the solution.
We came here for a solution.
Let's just solve the points and go back.
The solution doesn't really need it.
It has to be one sided.
You have this knowledge.
Propose.
It should be one sided.
Please propose your solution.
Sir, you cannot say that you put us in that trouble right now.
And you cannot expect that.
It has to be both sided.
Sir, you put us in that trouble.
This cannot be one sided, you mean?
You have to be two sided.
I had a few months back, where I thought I have orders.
We will proceed for the handover.
After 3-4 months, we are sitting again and digging the new thing.
Sir, Dhanu...
So, in retrospective, when I am thinking about it,
it looks like a trap for the association.
You created a trap in which you wanted to get ahead with contracts
which were signed for 12 months on a agreed price.
But you wanted the money to be transferred,
so that your responsibility goes for the talks.
This is what you did.
Good.
What is address close?
I think you have got that list.
Discussion.
Discussion.
Discussion.
What was he saying?
He had...
Hey man...
What was close?
Do you guys have any kind of proof or letter or discussion?
Hey man, this is not a threat.
This is not a threat.
Lot of people have been saying,
we should go to social media, share or stoning.
You know, you will say, it's okay, you are going to do that.
It is going to hurt both parties.
Us?
No, no.
We are prepared for that.
You are ordered to do that.
You please go ahead and do that.
We will have to do that.
We will have to do that because that is the only option left now.
If this conversation doesn't get any...
Even to the news site where you are...
We don't mind sitting there.
That's not a problem.
We will come to the new office.
We will have a proof or direction.
We are prepared.
How do we do that?
Have a fruitful discussion, sir.
No, fruitful discussion.
Have a...
That's not a problem.
We have to do that.
We have to do that.
We have to do that.
This is interesting.
See, we are not here to argue.
We need a solution.
Yeah.
If you are coming in the good solution,
it will be very good for you.
Solution is for coming in the good solution.
See, this is not a one-of-the-selection winner.
It is for its own reputation.
Yeah.
Its own brand name.
Okay.
You think on that perspective and you send the solution.
And it will be better for your all-existing project,
completing project, also it will be helpful in...
And this is not negotiation, sir.
We are asking for a fair deal for us.
We are not negotiating.
No, no, no.
Yes.
No, no, no, no.
One minute.
One minute.
Sir, when I bought the flat,
I was...
Even I think Jimmy was there on that day.
When I bought the...
Today I booked my flat there.
Okay.
Anup sir was there.
He himself assured me.
I told him,
he assured me.
He assured me.
He will fill this load.
Tell me, you know,
make more...
You know,
give it to yourself.
You trust me.
Anup...
Anup sir.
Anup sir.
Anup sir.
Okay,
what is your proposal
on point number one?
Wait, wait.
No, no, we will keep on discussing this.
Let's close.
Let's already propose.
What's your final proposal
on point number one?
Final.
What's your final proposal?
Data.
OK,
I will make it...
One point, please,
one point.
Please go ahead, please go ahead.
Go ahead, go ahead.
Go ahead.
I want to understand from Junay. Junay you are telling that from starting that you know financial handover we will do.
Still Hasat handover separately we want to do with the 115.
Can you tell me that are you going to do that Hasat handover? GPL, separately with association.
Or have you already transferred the Hasat handover to GLP?
It's already transferred to GLP.
That's a misleading information.
Now from August you are telling that the moment we do a financial handover you get all control.
Hypothetically I am saying if August we accepted that by now even Hemant won't come here.
But Hemant won't entertain us to sit here because still only money is with the GPL.
You want to handover that's why we are getting an option to sit here.
So lot of misleading information was happening.
Initially Junay see we talk it right many times.
We clearly said that we will do list each association.
Even association was under the same assumption. That was even shocking for us when we got to know.
Even I called, even night called, SCP, DG, everything we will list out.
And one by one we will list out.
So now what happened recently I was reading one document.
Hasat has already handed over to the managing company GLP and the GPL is reporting to association.
Lot of misleading information.
Even on that RERA website it was uploaded that we have handed over.
RERA website.
It is not that.
Yeah I mean it has been handed over to association which was an incorrect statement.
It was it.
It was like that.
Okay let's.
That's the point that Ganesh mentioned right.
Will you not agree with him?
You were saying in our first meeting you said you take the money in your hand.
We will still manage.
Asset will not be handed over. Asset handover is different than the action handover.
Did you not say that?
I said it but it is the GLP asset currently.
Why did we not mention that?
So what you said is one thing like you can see the gym.
You can walk around. You can see the swimming pool.
Then we will do the audit.
We will sign for each and every asset.
What you said is then again suddenly out of nowhere in October you are coming.
Fund is getting over. Fund is getting over. Take handover.
And then asset handover has already happened.
See for that.
And then we got the letter of RERA.
One more second.
The name was there.
Association was handed over.
We wrote so many emails on it.
We wrote so many emails. We spoke to you as a zero reply.
Last meeting with him.
With whom?
Last meeting.
We did not meet him.
When did we meet him?
He came and there was an association.
But it was not a clear justification.
What they said is every month we have to upload.
We have to update RERA on what is done.
So they have just uploaded it.
But somewhere we told them that it is incorrect.
I mean you have just put a fault.
Misleading information on the relevance.
Somebody filed a RERA.
Yes. It is a misleading site.
Once they are not there.
This is the key point.
We need a competent lawyer and a chartered taxon.
Let's just put in here.
See for that.
A competent neighbor shared invoices.
No, no. But we should not stop them.
We have see.
They denied to produce the bills.
We still have that issue.
Let's not talk about all this here.
We will go home and do it.
Let's fight them.
And he is still here.
He is still here.
He is still here.
We will get you first.
First of all we need to answer the maintenance staff.
Second, we need to complete the work before the financial handover.
We need to check the letter.
I have to get the transfer.
We have told them one more story.
That we should do all of it.
But for the photo we need funds, right?
So we told them that we would get a letter from lawyer.
which we will mention clearly that even after 12 months, we do the independent audit on our own.
You are responsible for finance.
I think we should do it.
I am treated.
They are back once again. Let's discuss.
Let's discuss.
I think we have done enough now.
Let's give a satisfactory answer for that.
Sir, I have told thrice.
What did you do?
Yes, I did.
Let's give a satisfactory answer.
Satisfactory, come with the cost.
I have already, I mean, let's be able to optimize some costs but not the cost.
Do you have any proposal?
We will have to sit and work on it.
We are sitting already, right?
Sir, today only we need more much. We should optimize.
What is the total manpower?
No, no, no.
We are not going outside from here.
Because, see, last time what you made, you said that lift we will salt.
In August meeting, you said everything will get salt.
We will put UPS.
You said we will put UPS.
No sir, it is not salt.
You went outside for the rest of the week.
No sir, sir, sir.
Not in UPS.
I mean, with the device, we will protect the whole UPS.
No, no, no.
But, no, no.
It was agreed that you will put UPS when Murad and Kamlaka...
Kamlaka Reddy and everyone worked together.
You did everything.
When you went out for the whole UPS, we waited for hours.
Evening itself, we got the email.
No emails.
10 minutes.
I will tell what Godrej means to Indian public.
My dad got married in 1966.
He has a Godrej armour sitting there.
He does polish in 1 to 10 years.
Still intact.
Now, I want to project how Godrej is right now and then tell the world.
That's what is going to happen.
We just making cash for the UPS.
I really want to think that.
Junaid knows me very well.
I spent once year on this flat without even visiting the site once.
Just with the name Godrej.
Yeah.
I have not visited once.
You know, somewhere that logic seemed in.
But that Godrej is all townish.
Right from what we feel.
So please, rebuild that before it goes on the fact.
We beg you.
Because you always think, you know, we are fighting, we are fighting.
We are not here to fight.
We love you, our position and seasons.
We will have purchase the flat like you.
What I would say is the same for a change.
Many of us will.
Do you want to say no, no, no, no.
What GPL guys told me is simple.
Ender means it's end of the day co-duration. End of the day it's co-duration.
You are in a different entity, I understand.
GNPL and GPL are the reason why we are sitting in this room and having this conversation.
As simple as that. I have taken a half day leave, you are working.
Because of that, because of GPL and GNPL, simple in my mind as a customer.
Correct.
You are the ones who should solve this for us.
You can't do it.
You don't have any more money from my money.
I don't have money.
And I have also done one more thing.
One second.
One second.
We have GPL contract renewal in February.
It's a right time, it's a right opportunity for us also as an owners.
And of course GPL since you guys are directly managing that relationship with them.
It's a time for them to renew the contract for GPL.
Why don't you guys, you are ready to bear half of the cost.
Why don't you put the remaining to GPL and tell them that it's just a matter of 20-25 lakhs.
Whereas we are okay.
And that's something which we can also discuss and we can assure them.
That if GPL agrees to bear that cost and provide us a proficient services for next one year.
We are ready to extend the fund.
With a better pricing.
With a competitor pricing.
The pricing.
I am not saying what I am deciding.
I am also saying what I am saying.
I am also saying everything.
What I am saying is, let us, yeah, so that's what, the first point only I said let us decide.
And if GPL agrees for a competitive pricing.
As per what we are receiving from other vendors.
That was my first statement Murli.
I said all of us decide.
If you don't listen then what will you do?
That's my request.
Because it's a time for a contract in the world.
If GPL agrees to our terms.
You guys extend the contract.
We are also here.
No commitments here.
We honours when deciding.
We honours when deciding.
It is not GPL's decision to speak on behalf of GPL.
I will have to speak to GPL director and take this.
It is not GPL's decision.
I understood.
Yesterday I had a call.
What GPL said is in the starting of March when you started.
You told them that this is the budget.
Suppose 2 crores.
2 crores is the budget.
You need to manage the complete society for 12 months.
Don't you have a document in which it can claim it from GPL for 50 lakh rupees.
Because they have done this deficit, right?
Okay, I have one.
So, as per Reira, the first one here we are paying the advance maintenance.
Both for sinking and the car pass fund.
So, as per Reira, this is the rest.
